Stellar Radiation is Critical for Regulating Star Formation and Driving Outflows in Low Mass Dwarf Galaxies

### 2019-03-22 thesis/chapters/ch_chapter1.tex
Rearranging figures a bit for style. Finished most of them but not complete. Need to double check that left/right (top/bottom) makes sense throughout

\begin{figure}
\centering
\includegraphics[width=0.975\linewidth]{figures/ch1/scale_height}
\caption{The total gas scale height at various times throughout the simulation. These times match the images in Figs.~\ref{fig:ch1:panel_x} and ~\ref{fig:ch1:panel_z}.}
\label{fig:ch1:scale_height}
\end{figure}

@@

\begin{figure*}
%\centering
\includegraphics[width=0.45\linewidth]{figures/ch1/phase_mass_fraction_evolution_log.png}
\includegraphics[width=0.45\linewidth]{figures/ch1/phase_volume_fraction_evolution_log.png}
\caption{The evolution of the mass and volume fractions for each phase of the model galaxy's ISM. See Appendix~\ref{appendix:phases} for definitions of each phase.}
\label{fig:ch1:ISM_evolution}
\end{figure*}

@@

\begin{figure}
\includegraphics[width=0.95\linewidth]{figures/ch1/G_o_profile} \\
\includegraphics[width=0.95\linewidth]{figures/ch1/ionizing_photon_profile}
\caption{
Azimuthally averaged radial profiles of the ISRF in the mid-plane of our galaxy in two different bands, time-averaged over 50 Myr from 300 -- 350~Myr. Here we define the midplane as within 2.5~$dx$ of z = 0, or 4.5~pc. The top panel gives $G_{\rm o}$, the flux of radiation between 6--13.6 eV normalized to the value in the solar neighborhood, shaded between minimum and maximum values at each position, with the average shown as a black line. The bottom panel gives the HI ionizing stellar radiation flux. Since this radiation is tracked directly through radiative transfer, the minimum value at all radii is 0 at some point. For this reason we only shade between the first quartile and maximum values. HeI ionizing radiation is very similar to HI ionizing radiation, with a small vertical offset, and is not shown for clarity. In the top panel, the minimum of the vertical axis is the UVB value of $G_o$.}
\label{fig:ch1:ISRF}
\end{figure}

\begin{figure*}
%\centering
\includegraphics[width=0.45\linewidth]{figures/ch1/g_o_2D_phase}
\includegraphics[width=0.45\linewidth]{figures/ch1/q_o_2D_phase}
\caption{Single-snapshot 2D radial profile plots at 300~Myr of the ISRF in two flux bands, $G_{\rm o}$ and HI ionizing radiation, illustrating the full dynamic range of radiation flux at a given radius in the galaxy. Here, we include all gas within the mid-plane of our dwarf galaxy. Since a majority of the mass of the galaxy is in the cold phase (see Fig.~\ref{fig:ch1:phase}), and is therefore optically thick to HI ionizing radiation, it does not show up in the HI ionizing radiation diagram. This gas readily appears in the $G_{\rm o}$ diagram since we assume it to be optically thin, though we do apply a localized shielding approximation.}
\label{fig:ch1:ISRF_2D}
\end{figure*}

@@

\begin{figure*}
\includegraphics[width=0.45\linewidth]{figures/ch1/total_mass_outflow}
\includegraphics[width=0.45\linewidth]{figures/ch1/total_mass_loading}
\caption{Spherical mass outflow rates (Eq.~[\ref{eq:dotM}]) and mass loading rates over time at 4 different radii from the galaxy.}
\label{fig:ch1:mass_outflow}
\end{figure*}

@@

\begin{figure}
\includegraphics[width=0.95\linewidth]{figures/ch1/velocity_distribution_time_average}
\caption{The time averaged radial velocity distribution of outflowing material external to the disk and within the virial radius of our dwarf galaxy. This is averaged over the same time interval as Fig.~\ref{fig:ch1:ISRF}. The outflowing material is multiphase, broken into WNM, WIM, and HIM. See Section~\ref{ch1:sec:phase} for definitions of these regimes. We note that WNM is often labeled simply as ``cold'', or gas below $T = 10^{4}$~K. There is little to no outflowing mass in the CNM.}
\label{fig:ch1:outflow_velocity}
\end{figure}

@@

\subsubsection{Metal Enriched Outflows}
Dwarf galaxies efficiently, and preferentially, eject metals released in stellar feedback from their shallow potential wells \citep{MacLowFerrara1999,FerraraTolstoy2000}. This has been better quantified recently both observationally \citep[e.g.][]{Kirby2011-metals,Zahid2012,Peeples2014,McQuinn2015} and with more detailed cosmological simulations \citep{Simpson2013,Angles-Alcazar2017,Muratov2017}. In the top panel of Fig.~\ref{fig:ch1:metal_evolution}, we give the metal mass loading factor for our galaxy over time, at the same radii as in Fig.~\ref{fig:ch1:mass_outflow}. The parameter used to quantify metal outflow efficiencies varies among works. Here, we define the metal mass loading factor as the metal outflow rate divided by the metal production rate, or
\begin{equation} \label{eq:eta-metal}
\eta_{\rm metal} = \frac{\dot{M}_{\rm metal}}{\rm{SFR} \times (M_{\rm metal}/M_{*})},
\end{equation}
where $\dot{M}_{\rm metal}$ is the metal mass outflow rate, $M_{\rm metal}$ is the total mass in metals produced, and $M_{*}$ is the total mass in stars. These metal loading factors fluctuate significantly with the SFR, just as was shown in Fig.~\ref{fig:ch1:mass_outflow}, reaching a minimum of about 0.05, but peaking at around 5. On average, over the simulation time, $\eta_{\rm metal}$ is below unity (around 0.5). Recent simulations of outflows from a Milky Way type disk indicate typical $\eta_{\rm metal}$ comparable to our results, usually between 0.5 and 1 \citep{Li2017,Fielding2017}. \cite{Muratov2017} computes a slightly different quantity for their galaxies, the normalized metal outflow rate $\eta_{Z} = \dot{M}_{\rm metal}/{\rm SFR}$, finding values of about 0.02 at 0.25~$R_{\rm vir}$ regardless of galaxy circular velocity. Our galaxy is consistent with this value, with an average $\eta_Z = 0.015$, fluctuating between 0.007 and 0.02.

\begin{figure}
\includegraphics[width=0.9\linewidth]{figures/ch1/metal_mass_loading} \\
\includegraphics[width=0.9\linewidth]{figures/ch1/metal_retention}
\caption{{\bf Top}: Metal mass loading factor (see Eq.[~\ref{eq:eta-metal}]) at the same radii as in Fig.~\ref{fig:ch1:mass_outflow}. This is the ratio between the metal outflow rate and the metal production rate. {\bf Bottom}: The fraction of metals contained in the disk, CGM, and outside the halo of our dwarf galaxy over time. In both panels, we consider the total mass of all individually tracked metal species, which is zero at initialization, not the aggregate total metallicity field, which is non-zero at initialization.}
\label{fig:ch1:metal_evolution}
\end{figure}

These large metal mass loading factors indicate that a majority of the metals produced in our dwarf galaxy are ejected from the disk. This is quantified in the lower panel of Fig.~\ref{fig:ch1:metal_evolution}, where we show the mass fraction of metals in the disk, circumgalactic medium (CGM), and outside the virial radius of our galaxy over time. After the first 20 Myr, SN-driven winds rapidly drive out large quantities of metals from the disk and into the galaxy's halo. This continues throughout the simulation, with only $\sim$4\% of produced metals residing in the disk of the galaxy. It only takes 150 Myr for some metals to reach the virial radius of the halo, with a steadily increasing fraction continually leaving the virial radius until about 350 Myr where the fraction levels off to just above 50\%. Likewise, the CGM metal content continually decreases until the end of the simulation from loss through the virial radius of the halo. See Section~\ref{ch1:sec:obs_metals} for further discussion.

@@

\begin{figure*}
\centering
\includegraphics[width=0.475\linewidth]{figures/ch1/all_gas_schmidt_law_evolution.png}
\includegraphics[width=0.475\linewidth]{figures/ch1/all_gas_efficiency_evolution.png}
\caption{The Kennicutt-Schmidt law (left) and extended Schmidt law (right) relationships for our galaxy as measured every megayear, plotted as points colored by time, with dark / purple early and light / green late. See text for details of the calculation. Recent observations from the SHIELD sample \protect\citep{Teich2016} are plotted as black points with error bars. On the left, we also give the best fit line to galaxies from the FIGGS sample from \protect\cite{Roychowdhury2014}, and on the right we also show the best fit line and 1 $\sigma$ errors from \protect\cite{Shi2011}. There is no clear correlation with time in this diagram.}
\label{fig:ch1:KS}
\end{figure*}

@@

\begin{figure}
\centering
\includegraphics[width=0.95\linewidth]{figures/ch1/fH2.png}
\caption{The final H$_2$ mass fraction in a grid of one-zone Grackle cooling models run with the same Grackle parameters and metallicity as our full hydrodynamics simulation. Each model is held at a uniform density $n = 10$~cm$^{-3}$. Each model varies either the H$^{-}$ photodetachment rate or the Lyman-Werner background over their respective UVB values by a given scale factor. Contours give factors of ten change in the H$_2$ fraction. We note the regime below 1.0 on each axis is somewhat unphysical, and is never reached in our hydrodynamics simulations.}
\label{fig:ch1:Grackle grid}
\end{figure}

@@

\begin{figure*}
\centering
\includegraphics[width=0.33\linewidth]{figures/ch1/sfr_resolution_study.png}
\includegraphics[width=0.33\linewidth]{figures/ch1/mass_evolution_resolution.png}
\includegraphics[width=0.33\linewidth]{figures/ch1/metal_retention_resolution.png}
\caption{A comparison of the SFR (left), disk gas mass (middle), and metal retention (right) evolution for our fiducial run (solid), 3.6~pc run (dotted), 3.6~pc run with a doubled initial supernova driving rate (dashed), and 7.2~pc run (dash-dotted). The line colors in the left panel are for better clarity between the SFRs.}
\label{fig:ch1:resolution_study}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.475\linewidth]{figures/ch1/3pc_phase.png}
\includegraphics[width=0.475\linewidth]{figures/ch1/6pc_phase.png}
\caption{Temperature-density phase diagrams for our 3.6~pc run (left) and 7.2~pc run (right), as presented for our fiducial run in Fig.~\ref{fig:ch1:phase}.}
\label{fig:ch1:phase_resolution}
\end{figure*}

>>>>

\begin{figure}
\centering
\includegraphics[width=0.75\linewidth]{figures/ch1/scale_height}
\caption{The total gas scale height at various times throughout the simulation. These times match the images in Figs.~\ref{fig:ch1:panel_x} and ~\ref{fig:ch1:panel_z}.}
\label{fig:ch1:scale_height}
\end{figure}

@@

\begin{figure*}
%\centering
\includegraphics[width=0.475\linewidth]{figures/ch1/phase_mass_fraction_evolution_log.png}
\includegraphics[width=0.475\linewidth]{figures/ch1/phase_volume_fraction_evolution_log.png}
\caption{The evolution of the mass and volume fractions for each phase of the model galaxy's ISM. See Appendix~\ref{appendix:phases} for definitions of each phase.}
\label{fig:ch1:ISM_evolution}
\end{figure*}

@@

\begin{figure}
\includegraphics[width=0.475\linewidth]{figures/ch1/G_o_profile}
\includegraphics[width=0.475\linewidth]{figures/ch1/ionizing_photon_profile}
\caption{
Azimuthally averaged radial profiles of the ISRF in the mid-plane of our galaxy in two different bands, time-averaged over 50 Myr from 300 -- 350~Myr. Here we define the midplane as within 2.5~$dx$ of z = 0, or 4.5~pc. The top panel gives $G_{\rm o}$, the flux of radiation between 6--13.6 eV normalized to the value in the solar neighborhood, shaded between minimum and maximum values at each position, with the average shown as a black line. The bottom panel gives the HI ionizing stellar radiation flux. Since this radiation is tracked directly through radiative transfer, the minimum value at all radii is 0 at some point. For this reason we only shade between the first quartile and maximum values. HeI ionizing radiation is very similar to HI ionizing radiation, with a small vertical offset, and is not shown for clarity. In the top panel, the minimum of the vertical axis is the UVB value of $G_o$.}
\label{fig:ch1:ISRF}
\end{figure}

\begin{figure}
%\centering
\includegraphics[width=0.475\linewidth]{figures/ch1/g_o_2D_phase}
\includegraphics[width=0.475\linewidth]{figures/ch1/q_o_2D_phase}
\caption{Single-snapshot 2D radial profile plots at 300~Myr of the ISRF in two flux bands, $G_{\rm o}$ and HI ionizing radiation, illustrating the full dynamic range of radiation flux at a given radius in the galaxy. Here, we include all gas within the mid-plane of our dwarf galaxy. Since a majority of the mass of the galaxy is in the cold phase (see Fig.~\ref{fig:ch1:phase}), and is therefore optically thick to HI ionizing radiation, it does not show up in the HI ionizing radiation diagram. This gas readily appears in the $G_{\rm o}$ diagram since we assume it to be optically thin, though we do apply a localized shielding approximation.}
\label{fig:ch1:ISRF_2D}
\end{figure}

@@

\begin{figure*}
\includegraphics[width=0.475\linewidth]{figures/ch1/total_mass_outflow}
\includegraphics[width=0.475\linewidth]{figures/ch1/total_mass_loading}
\caption{Spherical mass outflow rates (Eq.~[\ref{eq:dotM}]) and mass loading rates over time at 4 different radii from the galaxy.}
\label{fig:ch1:mass_outflow}
\end{figure*}

@@

\begin{figure}
\centering
\includegraphics[width=0.75\linewidth]{figures/ch1/velocity_distribution_time_average}
\caption{The time averaged radial velocity distribution of outflowing material external to the disk and within the virial radius of our dwarf galaxy. This is averaged over the same time interval as Fig.~\ref{fig:ch1:ISRF}. The outflowing material is multiphase, broken into WNM, WIM, and HIM. See Section~\ref{ch1:sec:phase} for definitions of these regimes. We note that WNM is often labeled simply as ``cold'', or gas below $T = 10^{4}$~K. There is little to no outflowing mass in the CNM.}
\label{fig:ch1:outflow_velocity}
\end{figure}

@@

\subsubsection{Metal Enriched Outflows}
Dwarf galaxies efficiently, and preferentially, eject metals released in stellar feedback from their shallow potential wells \citep{MacLowFerrara1999,FerraraTolstoy2000}. This has been better quantified recently both observationally \citep[e.g.][]{Kirby2011-metals,Zahid2012,Peeples2014,McQuinn2015} and with more detailed cosmological simulations \citep{Simpson2013,Angles-Alcazar2017,Muratov2017}. In the left panel of Fig.~\ref{fig:ch1:metal_evolution}, we give the metal mass loading factor for our galaxy over time, at the same radii as in Fig.~\ref{fig:ch1:mass_outflow}. The parameter used to quantify metal outflow efficiencies varies among works. Here, we define the metal mass loading factor as the metal outflow rate divided by the metal production rate, or
\begin{equation} \label{eq:eta-metal}
\eta_{\rm metal} = \frac{\dot{M}_{\rm metal}}{\rm{SFR} \times (M_{\rm metal}/M_{*})},
\end{equation}
where $\dot{M}_{\rm metal}$ is the metal mass outflow rate, $M_{\rm metal}$ is the total mass in metals produced, and $M_{*}$ is the total mass in stars. These metal loading factors fluctuate significantly with the SFR, just as was shown in Fig.~\ref{fig:ch1:mass_outflow}, reaching a minimum of about 0.05, but peaking at around 5. On average, over the simulation time, $\eta_{\rm metal}$ is below unity (around 0.5). Recent simulations of outflows from a Milky Way type disk indicate typical $\eta_{\rm metal}$ comparable to our results, usually between 0.5 and 1 \citep{Li2017,Fielding2017}. \cite{Muratov2017} computes a slightly different quantity for their galaxies, the normalized metal outflow rate $\eta_{Z} = \dot{M}_{\rm metal}/{\rm SFR}$, finding values of about 0.02 at 0.25~$R_{\rm vir}$ regardless of galaxy circular velocity. Our galaxy is consistent with this value, with an average $\eta_Z = 0.015$, fluctuating between 0.007 and 0.02.

\begin{figure}
\includegraphics[width=0.475\linewidth]{figures/ch1/metal_mass_loading}
\includegraphics[width=0.475\linewidth]{figures/ch1/metal_retention}
\caption{{\bf Left}: Metal mass loading factor (see Eq.[~\ref{eq:eta-metal}]) at the same radii as in Fig.~\ref{fig:ch1:mass_outflow}. This is the ratio between the metal outflow rate and the metal production rate. {\bf Right}: The fraction of metals contained in the disk, CGM, and outside the halo of our dwarf galaxy over time. In both panels, we consider the total mass of all individually tracked metal species, which is zero at initialization, not the aggregate total metallicity field, which is non-zero at initialization.}
\label{fig:ch1:metal_evolution}
\end{figure}

These large metal mass loading factors indicate that a majority of the metals produced in our dwarf galaxy are ejected from the disk. This is quantified in the right panel of Fig.~\ref{fig:ch1:metal_evolution}, where we show the mass fraction of metals in the disk, circumgalactic medium (CGM), and outside the virial radius of our galaxy over time. After the first 20 Myr, SN-driven winds rapidly drive out large quantities of metals from the disk and into the galaxy's halo. This continues throughout the simulation, with only $\sim$4\% of produced metals residing in the disk of the galaxy. It only takes 150 Myr for some metals to reach the virial radius of the halo, with a steadily increasing fraction continually leaving the virial radius until about 350 Myr where the fraction levels off to just above 50\%. Likewise, the CGM metal content continually decreases until the end of the simulation from loss through the virial radius of the halo. See Section~\ref{ch1:sec:obs_metals} for further discussion.

@@

\begin{figure*}
\centering
\includegraphics[width=0.5\linewidth]{figures/ch1/all_gas_schmidt_law_evolution.png}\\
\includegraphics[width=0.5\linewidth]{figures/ch1/all_gas_efficiency_evolution.png}
\caption{The Kennicutt-Schmidt law (top) and extended Schmidt law (bottom) relationships for our galaxy as measured every megayear, plotted as points colored by time, with dark / purple early and light / green late. See text for details of the calculation. Recent observations from the SHIELD sample \protect\citep{Teich2016} are plotted as black points with error bars. On the left, we also give the best fit line to galaxies from the FIGGS sample from \protect\cite{Roychowdhury2014}, and on the right we also show the best fit line and 1 $\sigma$ errors from \protect\cite{Shi2011}. There is no clear correlation with time in this diagram.}
\label{fig:ch1:KS}
\end{figure*}

@@

\begin{figure}
\centering
\includegraphics[width=0.75\linewidth]{figures/ch1/fH2.png}
\caption{The final H$_2$ mass fraction in a grid of one-zone Grackle cooling models run with the same Grackle parameters and metallicity as our full hydrodynamics simulation. Each model is held at a uniform density $n = 10$~cm$^{-3}$. Each model varies either the H$^{-}$ photodetachment rate or the Lyman-Werner background over their respective UVB values by a given scale factor. Contours give factors of ten change in the H$_2$ fraction. We note the regime below 1.0 on each axis is somewhat unphysical, and is never reached in our hydrodynamics simulations.}
\label{fig:ch1:Grackle grid}
\end{figure}

@@

\begin{figure*}
\centering
\includegraphics[width=0.475\linewidth]{figures/ch1/sfr_resolution_study.png}
\includegraphics[width=0.475\linewidth]{figures/ch1/mass_evolution_resolution.png}\\
\includegraphics[width=0.475\linewidth]{figures/ch1/metal_retention_resolution.png}
\caption{A comparison of the SFR (left), disk gas mass (middle), and metal retention (right) evolution for our fiducial run (solid), 3.6~pc run (dotted), 3.6~pc run with a doubled initial supernova driving rate (dashed), and 7.2~pc run (dash-dotted). The line colors in the left panel are for better clarity between the SFRs.}
\label{fig:ch1:resolution_study}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.75\linewidth]{figures/ch1/3pc_phase.png}\\
\includegraphics[width=0.75\linewidth]{figures/ch1/6pc_phase.png}
\caption{Temperature-density phase diagrams for our 3.6~pc run (left) and 7.2~pc run (right), as presented for our fiducial run in Fig.~\ref{fig:ch1:phase}.}
\label{fig:ch1:phase_resolution}
\end{figure*}
